Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-05 cordillera-cycle.tex
Correct small bugs.
Update figures and captions in manuscript.

% fig:locmap
\begin{figure}
  \includegraphics{locmap}
  \caption{Location map. In construction.}
  \label{fig:locmap}
\end{figure}

% fig:atm
\begin{figure}
  \includegraphics{atm}
  \caption{Monthly mean near-surface air temperature, precipitation and
           standard deviation of daily mean temperature for January and July
           months from the North American Regional Reanalysis (NARR)
           climatology, used as input fields to the ice sheet model. Note the
           strong contrasts in seasonality, timing of the precipitation peak,
           and temperature variability over the model domain, notably between
           the maritime and continental regions.}
  \label{fig:atm}
\end{figure}

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{\textbf{(top)} temperature offset time-series from ice and sediment
           core records used as palaeo-climate forcing for the ice sheet model
           (Table~\ref{tab:records}). \textbf{(bottom)} Modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent. The grey spans indicate the ranges of modelled times of
           glacial extrema corresponding to MIS~4 (61.9--55.4\,\unit{kyr}), 3
           (52.2--45.6\,\unit{kyr}), and 2 (last glacial maximum,
           29.5--16.9\,\unit{kyr}).
           \note{The dotted line represents an ongoing 5km-resolution
           simulation, which may be eventually be used in
           Figs.~\ref{fig:duration} and \ref{fig:deglac}.}}
  \label{fig:timeseries}
\end{figure}

% fig:snapshots
\begin{figure}
  \includegraphics{snapshots}
  \caption{Snapshots of modelled ice surface topography (500\,\unit{m}
           contours) at modelled times of glacial
           extrema, corresponding to MIS~4, 3, and 2.}
  \label{fig:snapshots}
\end{figure}

% fig:lgm
\begin{figure}
  \includegraphics{lgm}
  \caption{Modelled ice surface topography (100\,\unit{m} contours) and
           velocity (\unit{m\,yr^{-1}}) corresponding to the last glacial
           volume maximum.}
  \label{fig:lgm}
\end{figure}

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           A contiguous ice cover spanning from the Alaska Range (AR) to the
           southern Coast Mountians (CM) and Rocky Mountains (RM) exists for
           about 28\,\unit{kyr} in the GRIP simulation and about 29\,\unit{kyr}
           in the EPICA simulation. Note the irregular colour scale. A central
           ice cover persists over the Skeena Mountains (SM) during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           generally corresponds to relatively short durations of ice cover.
  \label{fig:duration}
\end{figure}

@@

>>>>

% fig:locmap
\begin{figure}
  \includegraphics{locmap}
  \caption{Relief map of northern North America showing a reconstruction of the
           areas once covered by the Cordilleran (CIS), Laurentide (LIS),
           Innuitian (IIS) and Greenland (GIS) ice sheets during the last
           18\,\unit{\chem{^{14}C}\,kyr\,BP} (21.4\,cal\,kyr\,BP)
           \citep{dyke-2004}. The rectangular box denotes the location of the
           modelling domain used in this study. Major mountain ranges covered
           by the ice sheet include the Alaska Range (AR), the Wrangell and
           St.-Elias mountains (WSE), the Selwyn and MacKenzie mountains (SMK),
           the Coast Mountains (CM) and the Rocky Mountains (RM). The background
           map consists of ETOPO1 \citep{data:etopo1} and Natural Earth Data
           \citep{data:naturalearth}.
           \todo{Mark palaeo-ice sheets and mountain ranges on the map.}}
  \label{fig:locmap}
\end{figure}

% fig:atm
\begin{figure}
  \includegraphics{atm}
  \caption{Monthly mean near-surface air temperature, precipitation and
           standard deviation of daily mean temperature for January and July
           months from the North American Regional Reanalysis (NARR)
           climatology, used to force the ice sheet model. Note the
           strong contrasts in seasonality, timing of the precipitation peak,
           and temperature variability over the model domain, notably between
           the maritime and continental regions.}
  \label{fig:atm}
\end{figure}

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and sediment core
           records (Table~\ref{tab:records}) used as palaeo-climate forcing for
           the ice sheet model \textbf{(top)}, and modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent \textbf{(bottom)}. Gray spans indicate Marine Isotope
           Stages (MIS) according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{lisiecki-raymo-2005}. Hatched
           rectangles indicate modelled ice volume extrema corresponding to
           MIS~4 (61.9--55.4\,\unit{kyr}), MIS~3 (52.2--45.6\,\unit{kyr}), and
           MIS~2 (last glacial maximum, 29.5--16.9\,\unit{kyr}).}
  \label{fig:timeseries}
\end{figure}

% fig:snapshots
\begin{figure}
  \includegraphics{snapshots}
  \caption{Snapshots of modelled surface topography (500\,\unit{m} contours)
           corresponding to the ice volume extrema indicated on
           Fig.~\ref{fig:timeseries}. Note the occurence of spatial similarities
           despite large differences in timing.}
  \label{fig:snapshots}
\end{figure}

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           A contiguous ice cover spanning from the Alaska Range (AR) to the
           southern Coast Mountians (CM) and Rocky Mountains (RM) exists for
           about 28\,\unit{kyr} in the GRIP simulation and about 29\,\unit{kyr}
           in the EPICA simulation. Note the irregular colour scale. A central
           ice cover persists over the Skeena Mountains (SM) during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           generally corresponds to relatively short durations of ice cover.}
  \label{fig:duration}
\end{figure}

% fig:warmbase
\begin{figure}
  \includegraphics{warmbase}
  \caption{Modelled duration of warm-based ice cover during the last
           120\,\unit{kyr}. Long ice cover durations combined with basal
           temperatures at the melting point may explain the strong glacial
           erosional imprint of the Skeena Mountains (SM) landscape. Hatches
           indicate areas that were covered by cold ice only.
           \note{indicate location of Skeena Mountains.}}
  \label{fig:warmbase}
\end{figure}

% fig:erosion
\begin{figure}
  \includegraphics{erosion}
  \caption{Modelled cumulative basal displacement (integrand of basal velocity)
           over the last 120\,\unit{kyr}.
           \note{Even after carefully adjusting the colours, I still find this
                 figure quite ugly and feel that it does not show much. I may
                 remove it from this paper and keep the idea for later use.}}
  \label{fig:erosion}
\end{figure}

@@

% fig:deglacshots
\begin{figure}
  \includegraphics{deglacshots}
  \caption{Snapshots of modelled surface topography (200\,\unit{m} contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial maximum (-19.5 kyr) and the last
           deglaciation.}
  \label{fig:deglacshots}
\end{figure}
